---
title: "End of Module Quiz (Module 6)"
output: learnr::tutorial
runtime: shiny_prerendered
description: "50 Days Data Science Course"
---

```{r setup, include=FALSE}
library(learnr)
library(stringr)
library(dplyr)
library(tidyr)
library(lubridate)
library(janitor)
library(mice)
knitr::opts_chunk$set(echo = FALSE)
```

## Day 6: Introduction to Data Cleaning

### Multichoice questions

```{r day6quiz }
quiz(
  caption = "Choose the correct answer from the provided options",
  question("Which function would you use to get a quick overview of missing values in your data frame?",
  answer("summary()", correct = TRUE),
  answer("plot()"),
  answer("mean()"),
  answer("filter()"),
  incorrect = "The summary() function provides statistics including NA counts for each column."
),

question("What does the is.na() function return when applied to a vector?",
  answer("The mean of the vector"),
  answer("A logical vector indicating NA positions", correct = TRUE),
  answer("The number of missing values"),
  answer("A cleaned version of the vector"),
  incorrect = "is.na() returns TRUE/FALSE values indicating missing data positions."
),

question("How would you identify duplicate rows in a data frame?",
  answer("duplicated(df)", correct = TRUE),
  answer("unique(df)"),
  answer("distinct(df)"),
  answer("drop_duplicates(df)"),
  incorrect = "The duplicated() function identifies duplicate rows."
),

question("Which of these is NOT a common data cleaning issue?",
  answer("Missing values"),
  answer("Outliers"),
  answer("Consistent formatting", correct = TRUE),
  answer("Incorrect data types"),
  incorrect = "Consistent formatting is desirable, not an issue to fix."
),

question("What does the str() function help you identify about your data?",
  answer("Only the column names"),
  answer("The structure including variable types", correct = TRUE),
  answer("The correlation between variables"),
  answer("The total number of observations"),
  incorrect = "str() shows structure including variable types and sample values."
),

question("How would you check for inconsistent capitalization in a character column?",
  answer("table(df$column)", correct = TRUE),
  answer("mean(df$column)"),
  answer("is.numeric(df$column)"),
  answer("dim(df)"),
  incorrect = "table() shows all unique values and their frequencies, revealing capitalization issues."
),

question("Which function would help identify numeric columns with unexpected character values?",
  answer("suppressWarnings(as.numeric())", correct = TRUE),
  answer("mean()"),
  answer("sum()"),
  answer("head()"),
  incorrect = "Trying to convert to numeric and checking for warnings helps identify problematic values."
)
)
```

### Question 1: Inspecting data

Load the mtcars dataset and inspect it using `head()`, `str()`, and `summary()`

```{r inspectdf, exercise = TRUE }


```

### Question 2: Identify Issues

Identify any potential issues in the dataset **(e.g., missing values, outliers)**.

```{r idissue, exercise = TRUE}

```

## Day 7: Handling Missing Data and Outliers

### Multichoice Questions

```{r day7quiz }
quiz(
  caption = "Choose the correct answer from the provided options",
  question("Which function would you use to completely remove rows with any NA values?",
  answer("na.omit()", correct = TRUE),
  answer("is.na()"),
  answer("na.replace()"),
  answer("drop.na()"),
  incorrect = "na.omit() removes rows with any NA values."
),

question("How would you replace NAs with the column mean using tidyverse?",
  answer("mutate(across(where(is.numeric), ~replace_na(., mean(., na.rm = TRUE)))", correct = TRUE),
  answer("drop_na()"),
  answer("na_mean()"),
  answer("fill.na()"),
  incorrect = "This mutate+across+replace_na pattern is the tidyverse way to replace NAs with means."
),

question("What is Tukey's Fence method used for?",
  answer("Identifying missing values"),
  answer("Detecting outliers", correct = TRUE),
  answer("Imputing data"),
  answer("Removing duplicates"),
  incorrect = "Tukey's Fence defines outliers as values outside Q1-1.5*IQR or Q3+1.5*IQR."
),

question("Which package provides advanced imputation methods for missing values?",
  answer("dplyr"),
  answer("mice", correct = TRUE),
  answer("tidyr"),
  answer("stringr"),
  incorrect = "The mice package provides Multiple Imputation by Chained Equations."
),

question("What does winsorization do to outliers?",
  answer("Removes them completely"),
  answer("Replaces them with NA"),
  answer("Caps them at a threshold value", correct = TRUE),
  answer("Log transforms them"),
  incorrect = "Winsorization caps extreme values at specified percentiles rather than removing them."
),

question("How would you calculate the IQR of a numeric vector x?",
  answer("IQR(x)", correct = TRUE),
  answer("mean(x)"),
  answer("sd(x)"),
  answer("range(x)"),
  incorrect = "IQR() calculates the interquartile range (Q3-Q1)."
),

question("When might log transformation be appropriate for outliers?",
  answer("When data is normally distributed"),
  answer("When data has exponential distribution", correct = TRUE),
  answer("When data has many zero values"),
  answer("When data is categorical"),
  incorrect = "Log transform helps with right-skewed data where values span several orders of magnitude."
)
)
```

### Question 1

Load the `airquality` dataset and print the output

```{r airquality, exercise = TRUE}

```

### Question 2

Identify and remove outliers in the `Ozone` column using either winsorization or threshold bound.

```{r matrix, exercise = TRUE}

```

### Question 3

Make a vector with 15 numbers, including one outlier (e.g., much larger than others). Plot it with boxplot().

```{r vecout, exercise = TRUE}


```

### Question 4

Create a data frame with 5 rows, including 2 NAs. Impute missing values with mice using the "mean" method.

```{r dfimpute, exercise = TRUE}


```

## Day 8: Strings and Date manipulations

```{r day8quiz }
quiz(
  caption = "Choose the correct answer from the provided options",
  question("Which package provides str_detect() for string pattern matching?",
               answer("lubridate"),
               answer("stringr", correct = TRUE),
               answer("dplyr"),
               answer("forcats"),
               incorrect = "stringr provides consistent string manipulation functions."
      ),
      
      question("How would you extract the first 3 characters from a string column?",
               answer("str_sub(column, 1, 3)", correct = TRUE),
               answer("str_extract(column, '^...')"),
               answer("str_split(column, 3)"),
               answer("str_trim(column, 3)"),
               incorrect = "str_sub() extracts substrings by position."
      ),
      
      question("Which lubridate function converts character to date?",
               answer("ymd()", correct = TRUE),
               answer("dmy_time()"),
               answer("date_convert()"),
               answer("as.date()"),
               incorrect = "ymd() and similar functions parse dates from strings."
      ),
      
      question("How would you remove whitespace from both ends of strings?",
               answer("str_trim()", correct = TRUE),
               answer("str_clean()"),
               answer("str_remove()"),
               answer("str_squish()"),
               incorrect = "str_trim() removes whitespace from start/end of strings."
      ),
      
      question("Which function would you use to standardize inconsistent date formats?",
               answer("parse_date_time()", correct = TRUE),
               answer("str_to_date()"),
               answer("uniform_date()"),
               answer("date_convert()"),
               incorrect = "parse_date_time() handles multiple date formats flexibly."
      ),
      
      question("How would you replace all digits in strings with 'X'?",
               answer("str_replace_all(string, '\\\\d', 'X')", correct = TRUE),
               answer("str_remove(string, '0-9')"),
               answer("str_delete(string, 'digits')"),
               answer("str_filter(string, '\\\\d')"),
               incorrect = "str_replace_all() with regex '\\d' matches and replaces digits."
      ),
      
      question("Which lubridate function calculates time intervals?",
               answer("interval()", correct = TRUE),
               answer("time_diff()"),
               answer("duration()"),
               answer("period()"),
               incorrect = "interval() creates time intervals for duration calculations."
      )
)

```

### Question 1

Create a vector of 4 messy names (e.g., " JOHN DOE", "mary-jane ", "JOhn_wiCK"). Use `str_to_title()` and `str_replace()` and `str_trim()` to clean them.
```{r messynames, exercise = TRUE}

```

### Question 2

Make a vector of 3 dates in different formats undefined (e.g., ("2023-01-15", "01/25/2023", "02.05.2023"). Parse them into dates using `parse_date_time()`
```{r parsingdate, exercise = TRUE}

```

### Question 3

Extract the month and year from your parsed dates using `month()` and `year()` from `lubridate`.
```{r extractdate, exercise = TRUE}

```


## Day 9: Data Wrangling and Transformation

### Multichoice Questions

```{r day9quiz }
quiz(
  caption = "Choose the correct answer from the provided options",
  question("Which dplyr verb would you use to select specific columns?",
              answer("filter()"),
              answer("select()", correct = TRUE),
              answer("mutate()"),
              answer("summarize()"),
              incorrect = "select() chooses columns by name or helper functions."
     ),
     
     question("How would you perform a left join between df1 and df2?",
              answer("left_join(df1, df2, by = 'key')", correct = TRUE),
              answer("merge_left(df1, df2)"),
              answer("join(df1, df2, type = 'left')"),
              answer("combine(df1, df2)"),
              incorrect = "left_join() keeps all rows from the first (left) data frame."
     ),
     
     question("Which tidyr function converts wide data to long format?",
              answer("pivot_wider()"),
              answer("pivot_longer()", correct = TRUE),
              answer("spread()"),
              answer("gather()"),
              incorrect = "pivot_longer() is the modern replacement for gather()."
     ),
     
     question("How would you create a new column based on existing ones?",
              answer("select()"),
              answer("rename()"),
              answer("mutate()", correct = TRUE),
              answer("arrange()"),
              incorrect = "mutate() creates new columns while preserving existing ones."
     ),
     
     question("Which function would separate '2023-01-15' into year, month, day columns?",
              answer("separate(date_col, into = c('year','month','day'), sep = '-')", correct = TRUE),
              answer("split(date_col, '-')"),
              answer("divide(date_col, parts = 3)"),
              answer("extract(date_col, c('y','m','d'))"),
              incorrect = "separate() splits one column into multiple at a delimiter."
     ),
     
     question("How would you summarize data by group means?",
              answer("df %>% group_by(category) %>% summarize(avg = mean(value))", correct = TRUE),
              answer("df %>% mean(value)"),
              answer("df %>% summarize_all(mean)"),
              answer("df %>% avg_by(category)"),
              incorrect = "group_by() + summarize() computes group-wise statistics."
     ),
     
     question("Which join keeps only rows with matching keys in both data frames?",
              answer("left_join()"),
              answer("right_join()"),
              answer("inner_join()", correct = TRUE),
              answer("full_join()"),
              incorrect = "inner_join() keeps only rows with matches in both tables."
     )
)
```

### `dplyr` exercise with `mtcars`

-   Find all 8-cylinder (`cyl`) cars with horsepower `(hp) > 150`
-   Create a new column: `miles per horsepower (mpg/hp)`
-   Calculate the average weight `(wt)` by cylinder `(cyl)`

```{r practicedplyr, exercise = TRUE}

```

### `tidyr` transformation with `iris`

-   Reshape the `iris` data to show `Species`, Measurement `(Sepal.Length, Petal.Length, etc)` and `Value`
-   Then pivot back to the original format

```{r practicedtidyr, exercise = TRUE}

```

### Merging data

-   Use the data `products` and `sales` created from the code below
-   Experiment with the different join types we have learnt so far and identify which join gives you:
    -   All sales including those for discontinued products
    -   Products that never sold

```{r practicemerge, exercise = TRUE}
# Products table
products <- tibble(
  product_id = c(1, 2, 3, 4, 5),
  product_name = c("Laptop", "Mouse", "Keyboard", "Monitor", "Printer"),
  status = c("Active", "Active", "Discontinued", "Active", "Discontinued")
)

# Sales table
sales <- tibble(
  sale_id = c(101, 102, 103, 104),
  product_id = c(1, 3, 3, 4),
  amount = c(1200.50, 150.75, 180.25, 300.00),
  sale_date = as.Date(c("2023-05-01", "2023-06-15", "2023-07-01", "2023-08-10"))
)
```
