---
title: "End of Module Quiz (Module 4)"
output: learnr::tutorial
runtime: shiny_prerendered
description: "50 Days Data Science Course"
---

```{r setup, include=FALSE}
library(learnr)
library(caret)
library(dplyr)
library(tidyr)
library(ggplot2)
library(MASS)
library(ROCR)
knitr::opts_chunk$set(echo = FALSE)
```

## Day 16: Hypothesis Testing

### Multichoice Questions

```{r day16quiz}
quiz(
  caption = "Choose the correct answer from the provided options",
  question("What is the null hypothesis in a two-sample t-test?",
         answer("The means of both groups are different"),
         answer("The means of both groups are equal", correct = TRUE),
         answer("The variance of both groups are equal"),
         answer("The distributions of both groups are identical"),
         incorrect = "The null hypothesis assumes no difference between groups."
  ),

  question("What does a p-value of 0.03 indicate?",
         answer("There's a 3% probability the null hypothesis is true"),
         answer("There's a 97% probability the alternative hypothesis is true"),
         answer("If the null were true, there's a 3% chance of seeing results this extreme", correct = TRUE),
         answer("The effect size is 0.03"),
         incorrect = "The p-value is the probability of observing the data (or more extreme) if the null is true."
  ),

  question("Which test would you use to compare the means of three measurements from the same individuals?",
         answer("Independent samples t-test"),
         answer("Paired t-test", correct = TRUE),
         answer("Chi-square test"),
         answer("One-way ANOVA"),
         incorrect = "Paired t-test is for repeated measurements on the same subjects."
  ),

  question("What is the alternative hypothesis in a chi-square test of independence?",
         answer("The variables are normally distributed"),
         answer("The variables are dependent/associated", correct = TRUE),
         answer("The variables have equal variance"),
         answer("The variables follow a specific distribution"),
         incorrect = "Chi-square tests whether two categorical variables are independent."
  ),

  question("When would you use a one-sample t-test?",
         answer("To compare two independent groups"),
         answer("To compare a sample mean to a known population mean", correct = TRUE),
         answer("To compare three or more groups"),
         answer("To test for normality"),
         incorrect = "One-sample t-test compares sample mean to a hypothesized value."
  ),

  question("What assumption is common to t-tests but not chi-square tests?",
         answer("Random sampling"),
         answer("Expected frequencies >5"),
         answer("Normally distributed data", correct = TRUE),
         answer("Categorical variables"),
         incorrect = "T-tests assume normally distributed data (or large samples)."
  )
)
```

### One-sample t-test

Perform a one-sample t-test on the `mtcars` `mpg` column to test if the **mean differs from 20**. Store the result in `t_result`.
```{r 1samplet, exercise = TRUE}


```

### Independent(2) sample t-test

Perform an independent samples t-test comparing `mpg` between automatic `(am=0)` and manual `(am=1)` cars in `mtcars`. Assume **unequal variances**.
```{r 2samplet, exercise = TRUE}


```

### Chi-Square test of independence

Perform a chi-square test of independence between `cyl` (number of cylinders) and `vs` (engine shape) in `mtcars`. Store the result in `chi_result`
```{r chisquare, exercise = TRUE}


```

### Paired t-test

Perform a **paired t-test** comparing the first and second measurements in the `sleep` dataset. the `extra` column contains increase in hours of sleep after given drug 1 and 2 (`group`) to 10 students.

```{r pairedt, exercise = TRUE}

```

## Day 17: Analysis of Variance (ANOVA)

### Multichoice Questions

```{r day17quiz}
quiz(
  caption = "Choose the correct answer from the provided options",
  question("What does ANOVA test?",
         answer("Differences between variances of groups"),
         answer("Differences between means of two groups"),
         answer("Differences between means of two or more groups", correct = TRUE),
         answer("Correlations between variables"),
         incorrect = "ANOVA compares means across multiple groups."
  ),

  question("What is the null hypothesis in one-way ANOVA?",
         answer("All group means are equal", correct = TRUE),
         answer("All group variances are equal"),
         answer("At least one group mean is different"),
         answer("The data are normally distributed"),
         incorrect = "ANOVA's null hypothesis is that all group means are equal."
  ),

  question("What does the F-statistic in ANOVA represent?",
         answer("The ratio of between-group to within-group variability", correct = TRUE),
         answer("The difference between largest and smallest means"),
         answer("The average variance across groups"),
         answer("The probability of Type I error"),
         incorrect = "F-statistic compares between-group to within-group variation."
  ),

  question("When would you use Tukey's HSD test?",
         answer("To test ANOVA assumptions"),
         answer("To compare all pairs of groups after significant ANOVA", correct = TRUE),
         answer("To transform non-normal data"),
         answer("To calculate effect size"),
         incorrect = "Tukey's HSD controls family-wise error rate in multiple comparisons."
  ),

  question("Which assumption is NOT required for ANOVA?",
         answer("Normally distributed residuals"),
         answer("Equal variances across groups"),
         answer("Independent observations"),
         answer("Equal sample sizes", correct = TRUE),
         incorrect = "ANOVA can handle unequal sample sizes (though balanced designs are preferred)."
  ),

  question("What does a significant Levene's test indicate about your ANOVA?",
         answer("The group means are different"),
         answer("The homogeneity of variance assumption is violated", correct = TRUE),
         answer("The data are not normally distributed"),
         answer("The sample size is too small"),
         incorrect = "Levene's test checks the equal variance assumption."
  )
)
```

### One-way ANOVA

Perform a **one-way ANOVA** testing if `mpg` differs by number of gears `(gear)` in `mtcars`. Store the result in `aov_result`.
```{r 1waynova, exercise = TRUE}

```

### Post-hoc Test

Perform **Tukey's HSD** test on the ANOVA result comparing `mpg` by cylinder count `(cyl)` in `mtcars`.
```{r tukeyhsd, exercise = TRUE}

```

### Checking ANOVA Assumptions

Check ANOVA assumptions by plotting the diagnostic plots for the `aov` model of `mpg` by `vs` or using Shapiro and Levennes test.
```{r asumnova, exercise = TRUE}

```


## Day 18: ML Basics - SL with Linear Regression

### Multichoice Questions

```{r day18quiz}
quiz(
  caption = "Choose the correct answer from the provided options",
  question("Which is NOT a type of machine learning?",
         answer("Supervised learning"),
         answer("Unsupervised learning"),
         answer("Reinforcement learning"),
         answer("Descriptive learning", correct = TRUE),
         incorrect = "The main types are supervised, unsupervised, and reinforcement learning."
 ),

 question("What is the primary goal of supervised learning?",
         answer("To discover hidden patterns in data"),
         answer("To learn a mapping from inputs to outputs", correct = TRUE),
         answer("To maximize rewards in an environment"),
         answer("To reduce data dimensionality"),
         incorrect = "Supervised learning learns from labeled examples to predict outcomes."
 ),

 question("Which caret function trains models?",
         answer("predict()"),
         answer("train()", correct = TRUE),
         answer("model()"),
         answer("fit()"),
         incorrect = "The train() function in caret handles model training."
 ),

 question("What does RMSE measure in regression?",
         answer("The correlation between predicted and actual values"),
         answer("The average magnitude of prediction errors", correct = TRUE),
         answer("The proportion of variance explained"),
         answer("The classification accuracy"),
         incorrect = "Root Mean Squared Error measures prediction error magnitude."
 ),

 question("Which is NOT a step in a typical ML workflow?",
         answer("Data preprocessing"),
         answer("Model training"),
         answer("Feature engineering"),
         answer("Hypothesis testing", correct = TRUE),
         incorrect = "While important, hypothesis testing isn't a core ML workflow step."
 ),

question("What does the 'preProcess' argument in caret's train() control?",
         answer("The model hyperparameters"),
         answer("The data preprocessing steps", correct = TRUE),
         answer("The performance metrics"),
         answer("The computational backend"),
         incorrect = "preProcess handles centering, scaling, imputation etc."
 )
)
```


### Linear regression

Train a **linear regression model** to predict `mpg` from `wt` in `mtcars` using `caret`. Store the model in `lm_model`
```{r linreg, exercise = TRUE}

```

### Evaluate model

Calculate **RMSE** and **R-squared** for predictions on the `mtcars` training set using the `lm_model` you created.
```{r evalmod, exercise = TRUE}

```

### Splitting data

Create a **70-30** train-test split of the `mtcars` data for `mpg` prediction. Use `set.seed(500)` and store train data in `train_data`.
```{r splitdat, exercise = TRUE}

```

### Cross-Validation

Train a linear regression model with **10-fold cross-validation** to predict `mpg` from `wt` and `hp` in `mtcars`.
```{r crossval, exercise = TRUE}

```

## Day 19: ML Basics - Classification with Logistic Regression

### Multichoice Questions
```{r day19quiz}
quiz(
  caption = "Choose the correct answer from the provided options",
  question("What type of dependent variable is required for logistic regression?",
         answer("Continuous numeric"),
         answer("Binary categorical", correct = TRUE),
         answer("Ordinal categorical"),
         answer("Any variable type"),
         incorrect = "Logistic regression requires a binary (two-category) outcome variable."
  ),

  question("What does the logistic function (sigmoid) transform?",
         answer("Input features to higher dimensions"),
         answer("Linear predictions to probabilities between 0 and 1", correct = TRUE),
         answer("Categorical variables to numeric values"),
         answer("Non-linear relationships to linear ones"),
         incorrect = "The sigmoid function converts the linear combination of predictors to a probability between 0 and 1."
  ),

  question("Which metric is NOT typically used to evaluate classification models?",
         answer("Accuracy"),
         answer("RMSE", correct = TRUE),
         answer("Recall"),
         answer("Specificity"),
         incorrect = "RMSE is used for regression, not classification problems."
  ),

  question("What does the AUC (Area Under Curve) represent in an ROC curve?",
         answer("The probability the model will make an error"),
         answer("The model's accuracy at all thresholds"),
         answer("The model's ability to distinguish between classes", correct = TRUE),
         answer("The optimal classification threshold"),
         incorrect = "AUC measures how well the model distinguishes between positive and negative classes across all thresholds."
  ),

  question("In a confusion matrix, what does recall measure?",
         answer("Correct positive predictions out of all positive predictions"),
         answer("Correct positive predictions out of all actual positives", correct = TRUE),
         answer("Correct negative predictions out of all negative predictions"),
         answer("Overall correctness of predictions"),
         incorrect = "Recall (sensitivity) measures how many actual positives were correctly identified."
  ),

  question("Which package provides comprehensive ROC curve plotting capabilities?",
         answer("ggplot2"),
         answer("ROCR", correct = TRUE),
         answer("caret"),
         answer("pROC"),
         incorrect = "ROCR is specifically designed for visualizing classifier performance."
  ),

  question("What does a precision of 0.8 mean?",
         answer("80% of positive predictions were correct", correct = TRUE),
         answer("80% of actual positives were identified"),
         answer("The model is correct 80% of the time"),
         answer("The false positive rate is 20%"),
         incorrect = "Precision measures the proportion of positive identifications that were correct."
  )
)

```

### Logistic regression

Train a **logistic regression** model to predict `vs` (engine type) from `mpg` and `wt` in `mtcars` using `caret`. Store as `logit_model`. (**Hint**: Convert `vs` to factor first).
```{r logreg, exercise = TRUE}


```
<div id="logreg-hint">
**Hint:** Use `method='glm'` and `family='binomial'` for logistic regression.
</div>

### Confusion Matrix

Generate predictions from `logit_model` on `mtcars` and create a **confusion matrix**. Store as `conf_mat`.
```{r confmat, exercise = TRUE}

```

### ROC curve with ROCR

Using `ROCR` package, create an **ROC curve** for the logistic regression model. First get predicted probabilities `(type='prob')`, then plot the ROC curve.
```{r ROC, exercise = TRUE}

```

### Calculate AUC

Calculate the **AUC** for the logistic regression model using `ROCR` package. Store the AUC value in a variable `auc_value`.
```{r AUC, exercise = TRUE}

```
<div id="logreg-hint">
**Hint:** Use `performance()` with `measure='auc'`
</div>
